### 2021-06-18 README.Rmd
change/update

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
library("tidyverse")
library(kableExtra)
library(peacesciencer)
library(stevemisc)
```

@@

#library(tidyverse)
#library(peacesciencer)
# library(stevemisc)
library(tictoc)

@@

# r2sd() is in {stevemisc}, a {peacesciencer} dependency.
Data %>%
  mutate_at(vars("cincprop", "mindemest", "minwbgdppc", "minmilit"),
            ~r2sd(.)) -> Data

summary(modDD <- glm(gmlmidonset ~ landcontig + cincprop + cowmajdyad + cow_defense +
               mindemest + minwbgdppc + minmilit +
               gmlmidspell + I(gmlmidspell^2) + I(gmlmidspell^3), data= Data,
             family=binomial(link="logit")))
toc()

@@

modCW <- list()
summary(modCW$"All UCDP Conflicts" <- glm(ucdponset ~ l1_wbgdppc2011est + l1_wbpopest  +
                    l1_xm_qudsest + I(l1_xm_qudsest^2) +
                    newlmtnest + ethfrac + relfrac +
                    ucdpspell + I(ucdpspell^2) + I(ucdpspell^3), data=subset(Data),
                  family = binomial(link="logit")))

summary(modCW$"Wars Only"  <- glm(war_ucdponset ~ l1_wbgdppc2011est + l1_wbpopest  +
                    l1_xm_qudsest + I(l1_xm_qudsest^2) +
                    newlmtnest + ethfrac + relfrac +
                    war_ucdpspell + I(war_ucdpspell^2) + I(war_ucdpspell^3), data=subset(Data),
                  family = binomial(link="logit")))

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r loadstuff, echo=FALSE, results="hide", message=FALSE}
library("badger")
library("tidyverse")
library(kableExtra)
library(peacesciencer)
library(stevemisc)
```

@@

# library(tidyverse) # load this first for most/all things
# library(peacesciencer) # the package of interest
# library(stevemisc) # a dependency, but also used for standardizing variables for better interpretation
library(tictoc)

@@

# r2sd() is in {stevemisc}, a {peacesciencer} dependency.
# This is just for a more readable regression output.
Data %>%
  mutate_at(vars("cincprop", "mindemest", "minwbgdppc", "minmilit"),
            ~r2sd(.)) -> Data

broom::tidy(modDD <- glm(gmlmidonset ~ landcontig + cincprop + cowmajdyad + cow_defense +
               mindemest + minwbgdppc + minmilit +
               gmlmidspell + I(gmlmidspell^2) + I(gmlmidspell^3), data= Data,
             family=binomial(link="logit")))
toc()

@@

modCW <- list()
broom::tidy(modCW$"All UCDP Conflicts" <- glm(ucdponset ~ l1_wbgdppc2011est + l1_wbpopest  +
                    l1_xm_qudsest + I(l1_xm_qudsest^2) +
                    newlmtnest + ethfrac + relfrac +
                    ucdpspell + I(ucdpspell^2) + I(ucdpspell^3), data=subset(Data),
                  family = binomial(link="logit")))

broom::tidy(modCW$"Wars Only"  <- glm(war_ucdponset ~ l1_wbgdppc2011est + l1_wbpopest  +
                    l1_xm_qudsest + I(l1_xm_qudsest^2) +
                    newlmtnest + ethfrac + relfrac +
                    war_ucdpspell + I(war_ucdpspell^2) + I(war_ucdpspell^3), data=subset(Data),
                  family = binomial(link="logit")))
